### 2018-10-22 src/1_Introduction.tex
correccion despues del examen

"An individual economic variable, viewed as a time series, can wander extensively
and yet some pairs of series may be expected to move so that they do not drift
far apart."-Robert F. Engle and Clive W.J. Granger~\cite{engle1987}.\\
In this introduction we present the scope, objectives, hypothesis and
organization of this thesis.

@@

The specific objectives of this research are,
\begin{itemize}
\item $\Large \mathcal{O}_1$: \emph{A review of the literature on time series
analysis models including machine learning techniques.}
\item $\Large \mathcal{O}_2$: \emph{Development of a set of known features of the
studied time series and the application to improve forecasting.}
\item $\Large \mathcal{O}_3$: \emph{Development of parallel and efficient
algorithms to ensure quick response times .}
\item $\Large \mathcal{O}_4$: \emph{Deep mathematical analysis of the proposal
and financial concepts involved.}
\item $\Large \mathcal{O}_5$: \emph{Design and implement representative set of
experiments in order to show when and why the proposal performs better.}
\end{itemize}

\section{Research Hypothesis}

Cointegration concept was introduced by Engle and Granger in 1987
\cite{engle1987} and implies that one or more linear combinations of
non-stationary variables are stationary even though individually they are not.
Moreover Stock and Watson in 1988 \cite{stock+watson1988} observed that
cointegration reflects the common stochastic trends providing a useful way to
understand cointegration relationships. These common stochastic trends can be
also interpreted as a long-run equilibrium relationships.

>>>>

``An individual economic variable, viewed as a time series, can wander extensively
and yet some pairs of series may be expected to move so that they do not drift
far apart.''-Robert F. Engle and Clive W.J. Granger~\cite{engle1987}.\\
In this introduction we present the scope, objectives, hypothesis and
organization of this thesis.

@@

The specific objectives of this research are,
\begin{itemize}[noitemsep,topsep=0pt]
\item $\Large \mathcal{O}_1$: \emph{A review of the literature on time series
analysis models including machine learning techniques.}
\item $\Large \mathcal{O}_2$: \emph{Development of a set of known features of the
studied time series and the application to improve forecasting.}
\item $\Large \mathcal{O}_3$: \emph{Development of parallel and efficient
algorithms to ensure quick response times .}
\item $\Large \mathcal{O}_4$: \emph{Deep mathematical analysis of the proposal
and financial concepts involved.}
\item $\Large \mathcal{O}_5$: \emph{Design and implement representative set of
experiments in order to show when and why the proposal performs better.}
\end{itemize}

\section{Research Hypothesis}
Cointegration concept was introduced by Engle and Granger in 1987
\cite{engle1987} and implies that one or more linear combinations of
non-stationary variables are stationary even though individually they are not.
Moreover, Stock and Watson in 1988 \cite{stock+watson1988} observed that
cointegration reflects the common stochastic trends providing a useful way to
understand cointegration relationships. These common stochastic trends can be
also interpreted as a long-run equilibrium relationships.
